SMT-Boosted Security Types for Low-Level MPC

### 2024-10-12 esop25/cpj.tex
checkpoint

\begin{definition}
  \label{definition-sound}
  Given $\prog$ with $\iov(\prog) = S \cup M \cup P \cup O$
  and $\flips(\prog) = R$, we say that
  \emph{$\Gamma$ is sound for $\prog$} iff for all $M' \subseteq M$
      and $x \in S \cup R$, the following
      conditions hold:
  \begin{enumerate}[\hspace{5mm}i.]
    \item  if $\setit{x}$ interferes with $M'$ then
      there exists $\ty$ with $\leakj{\Gamma}{M'}{\ty}$ and $x \in \ty$.
    \item  if there exists  $X \subseteq S \cup R$ such that
      $\setit{x}$ interferes with $M'$ conditionally on $X$,
      then $\leakj{\Gamma}{M'}{\ty}$ and
      $\leakclose{\Gamma}{\ty \cup X}{\ty'}$ and
      $\setit{x} \in \ty'$.
  \end{enumerate}
\end{definition}

>>>>

\begin{definition}
  \label{definition-sound}
  Given $\prog$ with $\iov(\prog) = S \cup M \cup P \cup O$
  and $\flips(\prog) = R$, we say that
  \emph{$\Gamma$ is sound for $\prog$} iff for all $M' \subseteq M$
      and $x \in S \cup R$, the following
      conditions hold:
  \begin{enumerate}[\hspace{5mm}i.]
    \item  if $\setit{x}$ interferes with $M'$ then
      there exists $\ty$ with $\leakj{\Gamma}{M'}{\ty}$ and $x \in \ty$.
    \item  if there exists  $X \subseteq S \cup R$ such that
      $\setit{x}$ interferes with $M'$ conditionally on $X$,
      then $\leakj{\Gamma}{M'}{\ty}$ and
      $\leakclose{\Gamma}{\ty \cup X}{\ty'}$ and
      $x \in \ty'$.
  \end{enumerate}
\end{definition}

### 2024-10-12 esop25/ipj.tex
checkpoint

\begin{definition}
  Given $H,C$ and $\prog$ with $\secrets(\prog) = S$ and $x \in \views(\prog)$,
  we say $x$ has an \emph{aberration} iff
  $\exists \adversary, \store \in \botruns(\prog)$ such that $\store(x) \ne \bot$
  and $\neg\exists \store' \in \runs(\prog) .
  \store_{S_H \cup \setit{x}} = \store'_{S_H \cup \setit{x}}$.
\end{definition}

@@

Our main type soundness result for integrity is then given as follows.
\begin{theorem}
  \label{theorem-ipj}
  Given pre-processing predicate $\eqspre$ and protocol $\prog$ with
  $\views(\prog) = V$, if
  $\ipj{\eqs}{\prog}{\Delta}$ is valid
  and for all $H,C$ with $\cheatj{\Delta}{H,C}{\seclev}$ 
  we have $\seclev(x) = \hilab$ for all $x \in \houtputs$, then $\prog$
  has integrity for all $H,C$.
\end{theorem}

>>>>

\begin{definition}
  Given $H,C$ and $\prog$ with $\iov(\prog) = S \cup V \cup O$,
  we say $x \in V \cup O$ has an \emph{aberration} iff
  $\exists \adversary, \store \in \botruns(\prog)$ such that
  $\store(x) \ne \bot$ and $\neg\exists \store' \in \runs(\prog)$
  with  $\store_{S_H} = \store'_{S_H}$ and
  $\store(x) = \lcod{\store',\be}{\cid}$ where
  $\xassign{x}{\be}{\cid} \in \prog$.
\end{definition}

@@

Our main type soundness result for integrity is then given as follows.
\begin{theorem}
  \label{theorem-ipj}
  Given  $\eqspre$ and $\prog$ with
  $\iov(\prog) = S \cup V \cup O$, if
  $\ipj{\eqs}{\prog}{\Delta}$ is valid
  and for all $H,C$ with $\cheatj{\Delta}{H,C}{\seclev}$ 
  we have $\seclev(x) = \hilab$ for all $x \in \houtputs \cup O_H$, then $\prog$
  has integrity for all $H,C$.
\end{theorem}
